---
title: "Gene Expression Variation Analysis (GEVA)"
author: "Nunes IJG, David MZ, Feltes BC, and Dorn M"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
   pdf_document:
     toc: true
     number_sections: true

vignette: >
  %\VignetteIndexEntry{GEVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
Sys.setlocale("LC_TIME","English_United States")
set.seed(1)
```

# Introduction

`GEVA` is a package for the analysis of differential gene expression in multiple experimental comparisons. It takes into account the fold-changes and p-values from previous differential expression (DE) results that use large-scale data (*e.g.*, microarray and RNA-seq) and evaluates which genes would react in response to the distinct experiments. This evaluation involves an unique pipeline of statistical methods, including weighted summarization, quantile detection, clustering, and ANOVA tests, in order to classify a subset of relevant genes whose differential expression is similar or dependent to certain biological factors.

This guide introduces the basic usage of `geva` package and focuses on its main features to perform the entire analysis from the input to the final classification. However, for more detailed specifications regarding classes, functions, and arguments from `geva`, please check the "Reference Guide" available in our GitHub repository. Alternatively, the local documentation can be accessed by typing `?geva` in the R console.

# Data Input

There's already a function that does the quick start.

# Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

# Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
